Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Do not yet reference text that may never get written
Extended conclusion, and other things

\noindent Cabals test feature can be used to automatically run tests~\cite{cabal}.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for Doctest and Hspec in a single cabal file.

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow} described in Section~\ref{sec:hspec-comb}.

@@

\noindent But it has several shortcomings:
It only works for exceptions with an {\tt Eq} instance,
but several standard exceptions (most
prominently {\tt ErrorCall}) have no {\tt Eq} instance.
It places an unnecessary {\tt Show} constraint on the
result of the {\tt IO} action, further limiting it's applicability.
It only allows to expect specific values; expecting
any exception of a certain type is not possible.

@@

\begin{itemize}
\item We discussed how to carry out BDD in Haskell.
\item We proposed to use Doctest for user documentation
and Hspec for code documentation.
\item We enhanced Haddock to support examples and properties,
and implemented Doctest integrated with QuickCheck.
\item We also supplied expectation combinators to Hspec.
\item With these two tools, specification can also be used for
documentation and automatic testing.
\item test discovery
\item This enhances the value of test code and would motivate
Haskell programmers to write test code.
\end{itemize}

>>>>

\noindent Cabal's test feature can be used to automatically run tests~\cite{cabal}.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for Doctest and Hspec in the same cabal file.

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow} described in Section~\ref{todo}.

@@

\noindent But it has several shortcomings:
It only works for exceptions with an {\tt Eq} instance,
but several standard exceptions (most
prominently {\tt ErrorCall}) have no {\tt Eq} instance.
And it places an unnecessary {\tt Show} constraint on the
result of the {\tt IO} action, further limiting it's applicability.
It only allows to expect specific values, expecting
any exception of a certain type is not possible.

@@

\begin{itemize}
\item
    We discussed how to apply BDD to Haskell.
\item
    We proposed to use Doctest for user documentation and Hspec for
    code documentation.
\item
    We added markup support for properties and examples to Haddock.
    And we implemented Doctest, to verify examples and test properties
    from Haddock comments.
\item
    We extend Hspec with a set of combinators for expectations.
\item
    With these two tools, specification can also be used for
    documentation and automatic testing.
\item
    We describe a mechanism, that can automatically discover all specs
    of a project.
\item
    We think that this enhances the value of test code, and we hope
    that it will motivate Haskell programmers to write more and better
    tests.
\end{itemize}
